---
title: "A quick tour of SOUP"
author: "Lingxue Zhu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A quick tour of SOUP}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette walks through two data examples and illustrates the basic usage of `SOUP`.

```{r}
library(devtools)
devtools::install_github("lingxuez/SOUP")
library(SOUP)
```

## Fetal Brain Data

### Gene selection

```{r}
cell.info = camp$cell.info
log.expr = log2(scaleRowSums(camp$counts)*(10^6) + 1)
log.expr = log.expr[, colnames(log.expr) %in% camp$select.genes]
dim(log.expr)
```

### SOUP clustering
```{r}
soup.out = SOUP(log.expr, Ks=c(2:5), type="log", nstart=50)
```

```{r}
heatmapKseq(soup.out$memberships, soup.out$Ks, cell.info$cell.type)
```

```{r}
K.use = 5
i.K = match(K.use, soup.out$Ks)

## pick the ending point: with the most N3 cells
soup.label = soup.out$major.labels[[i.K]]
k.end = which.max(table(soup.label, cell.info$cell.type)[, "N3"])
soup.timeline = getTimeline(membership = soup.out$memberships[[i.K]],
                            centers = soup.out$centers[[i.K]],
                            k.end=k.end)
## visualize timeline
genelist = c("CCNB1", "PAX6", "SOX2", "NEUROD6", "MEF2C")
plotMultipleGeneTimeline(expr=log.expr, 
                         genelist=genelist,
                         timeline=soup.timeline, 
                         nrow=2, ncol=3)
```

### Cross Validation


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
